### 2018-06-08 1_intro.tex
cleanup some.

\section{Related work}
\label{ch:intro:related}

@@

All the tools listed above consider only a single memory model, however, in real life we face serious engineering problems involving more than one execution environment.
One of these problems is the \textit{portability analysis} of the program from one hardware architecture to another.
A program written in a high-level language is compiled for different hardware architectures.
Even if all the compiler optimisations were disabled (which is a rare case nowadays), the behaviour of two compiled versions of the same program may differ due to differences between hardware memory models.
As the result, a program compiled for the platform $\mathcal{T}$ can reach states that are unreachable on the platform $\mathcal{S}$, which is a \textit{portability bug} from the source platform $\mathcal{S}$ to the target platform $\mathcal{T}$~\cite{Porthos17a}.

>>>>

\ifdefined\IsAalto
\else
  \vspace*{1em}
\fi
\section{Related work}
\label{ch:intro:related}

@@

All the tools listed above consider only a single memory model, however, in real life we face serious engineering problems involving more than one execution environment.
One of these problems is the \textit{portability analysis} of the program from one hardware architecture to another.
A program written in a high-level language is compiled for different hardware architectures.
Even if all the compiler optimisations were disabled (which is a rare case nowadays), the behaviour of two compiled versions of the same program may differ due to differences between hardware memory models.
As the result, a program compiled for the platform~$\mathcal{T}$ can reach states that are unreachable on the platform~$\mathcal{S}$, which is a \textit{portability bug} from the source platform~$\mathcal{S}$ to the target platform~$\mathcal{T}$~\cite{Porthos17a}.

### 2018-06-08 4_impl.tex
cleanup some.

The label resolution is necessary for establishing links to labelled statements.
In C, labelled statements are declared via the colon-syntax `\lstinline{<label>\;:\;<statement>}', and the labels are referenced by the jump-statement `\lstinline{goto\;<label>}'.
The label resolution algorithm traverses the \ytree{} and collects all declared labels into a map \texttt{JumpsResolver} that points a label to the labelled statement.
This information is used during compilation to set up unconditional jumps.

>>>>

The label resolution is necessary for establishing links to labelled statements.
In C, labelled statements are declared via the colon-syntax `\lstinline{<label> : <statement>}', and the labels are referenced by the jump-statement `\lstinline{goto <label>}'.
The label resolution algorithm traverses the \ytree{} and collects all declared labels into a map \texttt{JumpsResolver} that points a label to the labelled statement.
This information is used during compilation to set up unconditional jumps.

### 2018-06-08 90_summary.tex
cleanup some.

  \item As the C language supports unconditional \texttt{goto}-jumps, the control-flow graph can have an arbitrary structure, which can not be modelled solely by the program AST, therefore \porthos[2] compiles the AST to the low-level hardware-agnostic program representation \xgraph{}.
  For that, we implemented the \textit{full C interpreter} discussed in Section~\ref{ch:impl:proc:x-compiler}.

@@

\item For justifying the correctness of the verification that bases on the result of the input program unrolling (via the new unrolling scheme discussed in Section~\ref{ch:impl:proc:x-unroll}), one might want to be aware whether the execution in the unrolled event-flow graph has run the loop a whole number or it was interrupted on non-last event of the loop.
This can be modelled with two kinds of sink events (completed and uncompleted) of the event-flow graph as it was discussed in Sections~\ref{ch:enc:bmc:cf} and~\ref{ch:impl:proc:x-unroll}.

>>>>

  \item As the C language supports unconditional \texttt{goto}-jumps, the control-flow graph can have an arbitrary structure, which can not be modelled solely by the program AST, therefore \porthos[2] compiles the AST to the low-level hardware-agnostic program representation \xgraph{}.
  For that, we implemented the \textit{full C~interpreter} discussed in Section~\ref{ch:impl:proc:x-compiler}.

@@

\item For justifying the correctness of the verification that bases on the result of the input program unrolling (via the new unrolling scheme discussed in Section~\ref{ch:impl:proc:x-unroll}), one might want to be aware whether the execution in the unrolled event-flow graph has run the loop a whole number or it was interrupted on non-last event of the loop.
This can be modelled with \textit{two kinds of sink events} (completed and uncompleted) of the event-flow graph as it was discussed in Sections~\ref{ch:enc:bmc:cf} and~\ref{ch:impl:proc:x-unroll}.
